Expert-In-The-Loop Causal Discovery: Iterative Model Refinement Using Expert Knowledge

### 2025-02-09 paper/main.tex
Updates

    \caption{A comparison of Markov Equivalence Class (MEC) learned using Adult
	    Income Dataset \citep{Becker1996} using different algorithms and
	    sample sizes. Edge colour represents the sample size used: Red
	    ($N=400$), and blue ($N=800$). (a) PC algorithm with a mutual
	    information based CI test, (b) PC algorithm with a residualization
	    based test \citep{Ankan2023}, (c) Hill Climb Search with Bayesian
	    Information Criterion (BIC) score. The learned model structure
	    varies significantly in each case.}
    \label{fig:intro}
\end{figure}

>>>>

    \caption{A comparison of Markov Equivalence Class (MEC) learned using Adult
	     Income Dataset \citep{Becker1996} using different causal discovery
	     algorithms and sample sizes. Edge colour represents the sample size
	     used: red ($N=400$), and blue ($N=800$). (a) PC algorithm with a
	     mutual information based CI test, (b) PC algorithm with a
    	     residualization based test \citep{Ankan2023}, (c) Hill Climb Search with
	     Bayesian Information Criterion (BIC) score. The learned model structure varies
             significantly in each case.}
    \label{fig:intro}
\end{figure}
